\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}

\begin{document}

\noindent
\textbf{Carl Mäsak}, \texttt{810915-5013} \\
Studentvägen 36, 752 34 Uppsala, Sweden \\
Phone: +46 73 0496935, +46 18 525122

\section*{Skills}

\begin{itemize}

\item Java (Eclipse/OSGi/SWT)

\item Perl 5 and 6

\item HTML/CSS/Javascript/XSLT

\item Bioinformatics

\item Writing and language

\item \LaTeX/typesetting

\item Layout/design (print and web)

\item Unix/Linux

\item vim/Eclipse

\item Open Source tools and methodology

\end{itemize}

\section*{Objective}

I'm aiming for a job as a software developer or instructor. Preferably a
position where I can make good use of my current knowledge to create stable,
usable and attractive software, or where I can help transfer such knowledge.

\section*{Work experience}

\begin{itemize}

\item 2002-2007 \textbf{Web master and systems administrator} at IBG, Uppsala
University. Built and maintained a CMS on top of Apache Cocoon.

\item 2002-2007 \textbf{Teaching assistant} at various mathematics and
programming courses at MIC and IT, Uppsala University.

\item 2007-2009 \textbf{Web master} at Karolinska Institutet. Set up and
maintained a set of wikis and other web applications for use in teaching.

\item 2007-\hspace{2em} \textbf{Software developer} at Farmaceutisk
biovetenskap, Uppsala University. Helping develop Bioclipse, an open-source
bioinformatics and cheminformatics platform. (Ongoing.)

\end{itemize}

\section*{Education}

\begin{itemize}

\item 1997-2001 \textbf{The NV programme} (extended with university-level
mathematics and Russian) at Hvitfeldtska gymnasiet, Gothenburg.

\item 2001-\hspace{2em} \textbf{Engineering programme in Bioinformatics} at
Uppsala University, Uppsala. (Ongoing.)

\end{itemize}

\section*{Languages}

Levels in parentheses are according to the Common European Framework
of Reference for Languages.

\begin{itemize}
\item Swedish (C2)

\item English (speaking: C1. hearing, reading, writing: C2)

\item French (speaking: A2. hearing, reading, writing: B1)

\item Chinese (speaking: A1. hearing, reading: A2. writing: B1)

\item Russian (hearing, speaking: A1. reading, discussing, writing: A2)

\item Latin (speaking: A1. hearing, writing: A2. reading: B1)

\item Esperanto (reading, speaking: B2. hearing, writing: C1)
\end{itemize}

\end{document}
